<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-08 MainAnalysis.Rmd
Cleaned up columns, added sigfigs

```{r, merge_pkfits, eval=FALSE}
all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
                                       "2compartment"=pk_output_2comp,
                                       "flat"=pk_output_flat),
                                        dtxsid.col = "DTXSID",
                                  species.col = "Species")
```

>>>>

```{r, merge_pkfits, eval=FALSE}
all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
                                       "2compartment"=pk_output_2comp,
                                       "flat"=pk_output_flat))
write.csv(all.fit.table, paste("inst/ext/all.fit.table.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```
